---
title: Earthdata Cloud Cookbook R Notebook Template (Quarto)
authors:
    - name: "Albert Einstein"
      orcid: XXXX....
      email: albert@science.org
      affiliation: University of Relativity
    - name: "Marie Curie"
      orcid: XXXX....
      email: marie@science.org
      affiliation: University of Radioactivity
date: "YYYY-MM-DD" # Last modified date. `last-modified` automatically generates the date when the doc gets rendered, but when rendering on GitHub Actions it will show the render date. (#336)
keywords: [sea-ice, netcdf, terra]
format:
  html: default

# nasa-metadata is a custom field for providing NASA-specific metadata
# Everything above here is standard Quarto metadata.
nasa-metadata:
    - data-collections:
        - collection1 # (conceptid, shortname, TBD which is the best to use)
        - collection2
    - spheres: [atmosphere, biosphere, cryosphere, geosphere, hydrosphere]
    - session-info: # sessionInfo() or sessioninfo::session_info(). Would want just the versions of packages.
    - notebook-type: [tutorial, how-to, data-recipe]
    - code-lang: r # `lang` is a top-level field for defining the written language, so we use `code-lang` to specify the programming language used in the notebook
    - tools: [earthdatalogin, STAC] # nasa-specific tools - for tagging
---

## Overview

If you have an introductory paragraph, lead with it here! Keep it short and tied to your material.
This is also a great place to add a relevant image.

If it works for your material, a great way to frame things is to use the [**POP**](https://rockwoodleadership.org/pop-everything-strategic-planning-in-30-seconds-or-less/) (Purpose, Outcomes, Process) framework:

- **Purpose:** What is the motivation for this tutorial? What problem does it solve?
- **Outcomes:** quick notes on what you'll learn and where the tutorial ends
- **Process:** maybe a time estimate, and/or where it was first taught?

## Learning objectives

List the main learning objectives here.

## Prerequisites

Following your overview, tell your reader what concepts, packages, or other background information they'll **need** before learning your material. Tie this explicitly with links to other pages here in Foundations or to relevant external resources. Remove this body text, then populate the Markdown table, denoted in this cell with `|` vertical brackets, below, and fill out the information following. In this table, lay out prerequisite concepts by explicitly linking to other Foundations material or external resources, or describe generally helpful concepts.

Label the importance of each concept explicitly as **helpful/necessary**.

| Concepts | Importance | Notes |
| --- | --- | --- |
| [earthdatalogin](https://boettiger-lab.github.io/earthdatalogin/) | Necessary | Required for accessing NASA Earthdata Cloud resources |
| [Understanding of NetCDF](https://foundations.projectpythia.org/core/data-formats/netcdf-cf) | Helpful | Familiarity with metadata structure |
| Project management | Helpful | |

- **Time to learn**: estimate in minutes. For a rough idea, use 5 mins per subsection, 10 if longer; add these up for a total. Safer to round up and overestimate.
- **System requirements**:
    - Populate with any system, version, or non-R software requirements if necessary
    - Otherwise use the concepts table above and the Imports section below to describe required packages as necessary
    - If no extra requirements, remove the **System requirements** point altogether

---

## Imports
Begin your body of content with another `---` divider before continuing into this section, then remove this body text and populate the following code cell with all necessary R library imports **up-front**:

```{r}
# library(earthdatalogin)
```

## Your first content section

This is where you begin your first section of material, loosely tied to your objectives stated up front. Tie together your notebook as a narrative, with interspersed Markdown text, images, and more as necessary,

```{r}
# as well as any and all of your code cells
print("Hello world!")
```

### A content subsection
Divide and conquer your objectives with Markdown subsections, which will populate the helpful navbar in Jupyter Lab and here in the Cookbook!

```{r}
# some subsection code
a <- c(1, 2, 3, 4, 5)
a + 2
```

### Another content subsection
Keep up the good work! A note, *try to avoid using code comments as narrative*, and instead let them only exist as brief clarifications where necessary.

## Your second content section
Here we can move on to our second objective, and we can demonstrate...

### A subsection to the second section

#### a quick demonstration

##### of further and further

###### header levels

Check out [**the Quarto Guide**](https://quarto.org/docs/guide/) for syntax and guidance on customizing your notebooks. Don't hesitate to ask questions if you have problems getting it to look *just right*.

## Last Section

You can add [callouts using quarto callout syntax](https://quarto.org/docs/authoring/callouts/) to highlight important information, provide helpful hints, or even just to add some fun and personality to your notebook. Here's an example of a note callout:

:::{.callout-note}
Your relevant information here!
:::


:::{.callout-tip}
A helpful hint.
:::

:::{.callout-warning}
Be careful!
:::

We also suggest checking out Quarto's [documentation](https://quarto.org/docs/computations/execution-options.html#output-options) on specifying code cell output options.

---

## Summary
Add one final `---` marking the end of your body of content, and then conclude with a brief single paragraph summarizing at a high level the key pieces that were learned and how they tied to your objectives. Look to reiterate what the most important takeaways were.

## Additional resources

Link to relevant external material, further reading, documentation, etc.

## References
Be rigorous in your citations and references as necessary. Give credit where credit is due.

You're done! Give yourself a quick review, a high five, and send us a pull request. A few final notes:

 - Restart R and re-run all chunks to confirm that your notebook will cleanly run from start to finish
 - Clear all output before committing your notebook, our machines will do the heavy lifting
 - Take credit! Provide author information in the metadata.
 - Give credit! Attribute appropriate authorship for referenced code, information, images, etc.
 - Only include what you're legally allowed: **no copyright infringement or plagiarism**

Thank you for your contribution!

## Acknowledgements

This template builds from the [Project Pythia Notebook Template](https://github.com/ProjectPythia/cookbook-template/blob/main/notebooks/notebook-template.ipynb), which was in turn inspired by [this template](https://github.com/alan-turing-institute/the-turing-way/blob/master/book/templates/chapter-template/chapter-landing-page.md) of the wonderful [The Turing Way](https://the-turing-way.netlify.app) Jupyter Book.
